%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{EXPERIENCE}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}


%---------------------------------------------------------
  \cventrynew
    {SAP India}  {\bf {Gurgaon, IN}}
    {\textnormal{\textit{Development Consultant  \hfill {September 2021 - Present}}}}
    {   
        \cvproject{South Africa's leading pharmacy chain}{
          % \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developing e-commerce as well as quick commerce stores for the SA's leading pharmacy chain, offering fast delivery options within 60 minutes.}
            \item {Developed and integrated with {\bf payment service providers} such as PayU, Ozow, and PayGate, enabling multiple payment methods including credit cards, EFT, and digital wallets, while managing payment failure scenarios and retries.}
            \item {Implemented order placement journey \& order processing workflows, ensuring seamless user experience.}
          % \end{cvitems}
        }
        \vspace{1mm}
        \cvproject{India's leading B2B fashion store}{
          % \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Contributed to the backend development of India’s leading B2B fashion commerce platform using {\bf SAP Commerce} at the core and dedicated Spring Boot based microservices for the primary functionalities.}
            \item{Designed the architecture for a Tag Engine microservice aimed at implementing tagging functionality, with scalability to accommodate over 3 million products, laying the groundwork for future development.}
            \item {{\bf Led a team} of four to implement the location-based pricing to allow the sellers to have different pricing for every cluster of PIN codes, thereby resulting in the average increase of 15\% in revenue for the sellers.}
            \item { {\bf Reduced the shipping costs by up to 50\%} by replacing the single warehouse design with the multi-warehouse approach and thus, allowing more than 100 thousand sellers to ship the item from warehouse nearest to the delivery location.}
            \item {Enhanced the product creation flow by implementing the {\bf parallel processing of product data} received from Kafka.}
          % \end{cvitems}
          }
    }
\vspace{10pt} 

\cventrynew
    {Nagarro Software}  {\bf {Gurgaon, IN}}
    {\textnormal{\textit{Software Engineer  \hfill {January 2019 - September 2021}}}}
    {
      \cvproject{UK's healthcare platform}{
          % \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Contributed to Spring Boot based microservices development, focusing on scalability, maintainability, and performance.}
            \item {Role included analyzing requirements, designing and developing REST APIs, and ensuring adherence to coding standards.}
            \item {Identified and addressed performance bottlenecks, contributing to the platform's responsiveness under varying workloads.}
          % \end{cvitems}
          }
    }
\vspace{10pt} 

%---------------------------------------------------------
\end{cventries2}


